Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-13 analysis/paper/paper.Rmd
Fix figure cross-references

Looking at the ratings for all 450 articles and given the differing number of articles each co-author evaluated, there was broad agreement with no discernible patterns showing a strong bias or cause for concern (Figure S1).
However, the analyses did account for different raters for each article by including this as a random effect.

@@

There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*® for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).

When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Table S2, Figure S3).

@@

There was no effect detected for year when predicting the availability of computational methods (Table S3, Figure S4).
However, 2018 was clearly different with more data being made available than all other years (Table S4; Figure S5).

There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Tables S5, S6 and Figures S6, S7).

>>>>

Looking at the ratings for all 450 articles and given the differing number of articles each co-author evaluated, there was broad agreement with no discernible patterns showing a strong bias or cause for concern (Figure S1).
However, the analyses did account for different raters (assignees) for each article by including this as a random effect.

@@

There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology*® for the sharing of computational methods (code); the effects of all parameters were undecided (Figure Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).

When predicting the availability of data availability as compared with *Phytopathology*®, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*®, but no effects were detectable in any other journal title (Figure \@ref(fig:journal-parameters)B, Table S2, Figure S3).

@@

There was no effect detected for year when predicting the availability of computational methods (Figure \@ref(fig:year-parameters)A, Table S3, Figure S4).
However, 2018 was clearly different with more data being made available than all other years (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).

There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Figures \@ref(fig:IF-parameters)A, \@ref(fig:IF-parameters)B; Tables S5, S6; Figures S6, S7).
